---
title: "Simulate Claims"
author: "Brian A. Fannin"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r echo=FALSE, message=FALSE}
library(dplyr)
```

## Overview

```{r}
library(imagine)
dfPolicy <- NewPolicies(500, 2010)
```

```{r}
mySeverity <- GammaHelper(10000, 0.5)
```

Note that we augment the policy table by adding a field for the number of claims.

## Simulate by evaluation date

This is basically chain ladder.

We'll create a very simple example with three evaluation dates, fixed frequency and fixed link ratios.

```{r}
evalDates <- seq.Date(as.Date("2010-12-31"), length.out = 3, by = "years")
fixedLinks <- list(FixedVal(2)
                   , FixedVal(1.5))
```

```{r }
dfClaimsFixed <- ClaimsByEvaluationDate(dfPolicy
                                        , Frequency = FixedVal(1)
                                        , Severity = FixedVal(100)
                                        , Links = fixedLinks
                                        , EvaluationDates = evalDates)
```

```{r echo=FALSE, message=FALSE}
dfDisplay <- dfClaimsFixed %>% 
  arrange(PolicyID) %>% 
  head()

knitr::kable(dfDisplay)
```

We can make things a bit more complicated by introducing variable link ratios

```{r }
normalLinks <- list(NormalHelper(2, 1, .7, 4)
                    , NormalHelper(1.5, .5, .7, 3))

dfVariableLinks <- ClaimsByEvaluationDate(dfPolicy
                                          , Frequency = FixedVal(1)
                                          , Severity = FixedVal(100)
                                          , Links = normalLinks
                                          , EvaluationDates = evalDates)
```

```{r echo=FALSE, message=FALSE}
dfDisplay <- dfVariableLinks %>% 
  arrange(PolicyID) %>% 
  head()

knitr::kable(dfDisplay)
```

And for lots of fun, let's use a Poisson frequency, gamma severity and variable links.

```{r }
set.seed(1234)
dfAllVariable <- ClaimsByEvaluationDate(dfPolicy
                                       , Frequency = PoissonHelper(1)
                                       , Severity = GammaHelper(10000, 0.5)
                                       , Links = normalLinks
                                       , EvaluationDates = evalDates)
```

```{r echo=FALSE, message=FALSE}
dfDisplay <- dfAllVariable %>% 
  arrange(PolicyID) %>% 
  head(10)

knitr::kable(dfDisplay)
```
